Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-09-30 latex/robdml.tex
tex

%%%%%%%%% ABSTRACT
\begin{abstract}
	Deep metric learning models, being vulnerable to adversarial
	attacks, have safety and security implications in applications.
	%
	Improving the adversarial robustness of a model against the attacks becomes
	an important problem.
	%
	The existing defense methods are based on adversarial training.
	%
	However, they \oo{(1) robustness (2) speed/cost. (3) sampling matters.}
	%
	In this paper, we \oo{TBD}.
	%
	The proposed method is validated on three commonly
	used deep metric learning datasets, namely CUB-200-2011, Cars-196,
	and Stanford Online Product.
	%
	Comprehensive experimental results show our method outperforms
	the existing defense methods.
\end{abstract}

@@

% contributions
In brief, our contribusions include:
%
\begin{enumerate}
	%
	\item Hardness manipulation is proposed for the adversarial training
		of triplet-based deep metric learning models, which avoids model
		collapse in the typical min-max adversarial training setting.
		\oo{We discover that blah}.
		Our proposed method achieves higher adversarial robustness compared
		to the state-of-the-art.
		%
\end{enumerate}

@@

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
	% background
	Deep metric learning, being vulnerable to adversarial
	attacks, has safety and security implications in its applications.
	% importance
	To counter these attacks, it is important to design adversarial
	defense methods to improve adversarial robustness of deep metric learning.
	% insight
	However, as deep metric model with triplet loss is prone to collapse with
	excessively hard samples, the previous methods refrain from using the
	classical min-max adversarial training paradigm, but also suffer from
	inefficiency.
	% our proposal
	In this paper, we argue that the sampling strategy has a significant
	impact on the adversarial training for triplet-based deep metric learning.
	% solution 1
	\oo{
	Based on this, we propose Hardness Manipulation 
	TODO
	However, they the influence of triplet sampling strategy during
	adversarial training, 
	(1) robustness (2) speed/cost. (3) sampling matters.}
	%
	In this paper, we \oo{TBD}.
	%
	The proposed method is validated on three commonly
	used deep metric learning datasets, namely CUB-200-2011, Cars-196,
	and Stanford Online Product.
	%
	Comprehensive experimental results show our method outperforms
	the existing defense methods.
\end{abstract}

@@

% contributions
In brief, our contribusions include:
%
\begin{enumerate}
	%
	\item Hardness manipulation is proposed for the adversarial training
		of triplet-based deep metric learning models, which avoids model
		collapse in the typical min-max adversarial training setting.
		\oo{We discover that blah}.
		Our proposed method achieves higher adversarial robustness compared
		to the state-of-the-art.
		%
	\item Gradual Adversary.
		%
	\item Benchmark existing metric learning loss functions with adversarial
		training for future reference.
\end{enumerate}

@@

\subsection{Hardness Manipulation}

\subsection{Gradual Adversary}
